---
title: "validate_afc"
author: "Qiwei Lin and Derek Ouyang"
date: "2024-10-29"
output: html_document
---

# Setup

```{r}
library(dplyr)
library(readr)
library(mltest)
library(furrr)
library(future)
library(tictoc)
library(stringr)
library(tidyr)
library(doParallel)
registerDoParallel(detectCores())

github_path <- ""
server_path <- ""
github_result_path <- paste0(github_path, "output/results/")
server_result_path <- paste0(server_path, "disaggregation/results/")
fig_path <- paste0(github_path, "output/figures/")
  
source(paste0(github_path, "scripts/name_cleaning_helper_functions.R"))
source(paste0(github_path, "scripts/imputation_helper_functions.R"))

clean_group_names <- list(
  "asian_indian"="Asian Indian",
  "chinese"="Chinese",
  "filipino"="Filipino",
  "japanese"="Japanese",
  "korean"="Korean", 
  "vietnamese"="Vietnamese"
)

geo_race_table_lst <- readRDS(paste0(github_path,"data/geography/geo_race_table.rds"))

ssa_name_mapping <- list(
	"C" = "chinese",
	"R" = "filipino",
	"J" = "japanese",
	"K" = "korean",
	"I" = "asian_indian",
  "V" = "vietnamese"
  )

ssa_surnames <- read_csv(paste0(github_path,"external_data/SSA_Surnames.csv")) %>% 
  mutate(
    type = recode(
      str_sub(type, 1, 1), 
      !!!unlist(ssa_name_mapping)
    )
  )

ssa_p_race_given_surname <- ssa_surnames %>% 
  mutate(values = 1) %>% 
  filter(!is.na(name),!is.na(type)) %>% 
  pivot_wider(
    names_from = "type",
    values_from = "values"
  ) %>% 
  mutate(across(
    everything(),
    ~replace_na(., 0)
  )) %>% 
  select(name,asian_indian,chinese,filipino,japanese,korean,vietnamese)
```

# Create validation set with AFC

This data processing can only be done with raw AFC data containing PHI.

```{r}
# patients <- read_csv(paste0(server_path,"BQ/Patient_0124.csv"))
# patient_race <- read_csv(paste0(server_path,"BQ/PatientRace_0124.csv"))
# 
# patients_dedup <- patients %>%
#   transmute(
#     patientuid,
#     first = first %>% str_format_removal() %>% gsub(" ","",.),
#     last = last %>% str_format_removal() %>% gsub(" ","",.)
#   ) %>%
#   distinct()
# 
# saveRDS(patients_dedup, paste0(server_path,"disaggregation/patients_dedup_0124.rds"))
# 
# race_dedup <- patient_race %>%
#   group_by(patientuid) %>%
#   summarize(
#     patientracecode = paste0(sort(unique(as.character(patientracecode))), collapse = ", "),
#     patientracetext = paste0(sort(unique(patientracetext)), collapse = ", ")
#   )
# 
# saveRDS(race_dedup, paste0(server_path,"share/pi/deho-pi/AFC/disaggregation/race_dedup_0124.rds"))
# 
# temp <- readRDS(paste0(server_path,"disaggregation/race_dedup_0124.rds")) %>%
#   left_join(readRDS(paste0(server_path,"disaggregation/patients_dedup_0124.rds")))
# 
# patient_race_asian <- temp %>%
#   mutate(
#     asian_indian =
#       (grepl("2029-7", patientracecode, ignore.case = T) |
#         grepl("india", patientracetext, ignore.case = T)) &
#       !grepl("american indian|american-indian|amer indian|ameri, india|alaska indian", patientracetext, ignore.case = T),
#     chinese = grepl("2034-7", patientracecode, ignore.case = T) |
#       grepl("chinese", patientracetext, ignore.case = T),
#     filipino = grepl("2036-2", patientracecode, ignore.case = T) |
#       grepl("filipino", patientracetext, ignore.case = T),
#     japanese = grepl("2039-6", patientracecode, ignore.case = T) |
#       grepl("japanese", patientracetext, ignore.case = T),
#     korean = grepl("2040-4", patientracecode, ignore.case = T) |
#       grepl("korean", patientracetext, ignore.case = T),
#     vietnamese = grepl("2047-9", patientracecode, ignore.case = T) |
#       grepl("vietnamese", patientracetext, ignore.case = T),
#     other_asian = grepl("2028-9", patientracecode, ignore.case = T) |
#       grepl("other asian", patientracetext, ignore.case = T),
#     other_race = grepl("2106-3|2054-5|1002-5|2079-2|2086-7|2080-0|2500-7|2131-1", patientracecode, ignore.case = T) |
#       grepl("white|black|africa|hawaii|guam|chamorro|samoa|pacific|native|american indian|american-indian|amer indian|ameri, india|alaska indian", patientracetext, ignore.case = T)
#   ) %>%
#   mutate(total = asian_indian + chinese + filipino + japanese + korean + vietnamese) %>%
#   filter(total > 0) %>%
#   mutate(
#     last_length = nchar(last),
#     first_length = nchar(first)
#   ) %>%
#   arrange(patientuid,last_length,first_length) %>%
#   filter(!duplicated(patientuid))
# 
# only_asian <- patient_race_asian %>%
#   filter(!other_race)
# 
# only_single_asian <- only_asian %>%
#   mutate(
#     total = asian_indian + chinese + filipino + japanese + korean + vietnamese + other_asian
#   ) %>%
#   filter(total == 1) %>%
#   transmute(
#     patientuid,
#     raceeth = case_when(
#       asian_indian ~ "asian_indian",
#       chinese ~ "chinese",
#       filipino ~ "filipino",
#       japanese ~ "japanese",
#       korean ~ "korean",
#       vietnamese ~ "vietnamese"
#     ),
#     patientracetext,
#     first,
#     last
#   ) %>% 
#   filter(!is.na(last))
# 
# patient_location <- read_csv(paste0(server_path,"BQ/GeneratedPatientBaseline_0124.csv"))
# 
# patient_location_dedup <- patient_location %>%
#   transmute(
#     patientuid,
#     dob,
#     state = fips_state,
#     county = paste0(fips_state, fips_county),
#     zip = zipcode,
#     tract = paste0(fips_state, fips_county, tract)
#   ) %>%
#   filter(!duplicated(patientuid))
# 
# patient_outcomes <- read_csv(paste0(server_path,"hesitancy/intermediate/csvs/condition_features_v4.csv.gz"))
# 
# patient_outcomes_dedup <- patient_outcomes %>%
#   select(patientuid, hypertension, diabetes, depression, cancer, chronickidneydisease, asthma) %>%
#   distinct() %>%
#   group_by(patientuid) %>%
#   summarize(across(
#     everything(),
#     ~sum(.)
#   )) %>%
#   mutate(across(
#     hypertension:asthma,
#     ~(ifelse(.>0,1,0))
#   ))
# 
# patient_measurements <- read_csv(paste0(server_path,"hesitancy/intermediate/csvs/measurement_features_v4_with_values.csv.gz"))
# 
# patient_measurements_dedup <- patient_measurements %>%
#   select(patientuid, diabetes, glucose, kidney, thyroid) %>%
#   distinct() %>%
#   group_by(patientuid) %>%
#   summarize(across(
#     everything(),
#     ~sum(.)
#   )) %>%
#   mutate(across(
#     diabetes:thyroid,
#     ~(ifelse(.>0,1,0))
#   ))
# 
# patient_procedures <- read_csv(paste0(server_path,"hesitancy/intermediate/csvs/procedures_features_v4_with_values.csv.gz"))
# 
# patient_procedures_dedup <- patient_procedures %>%
#   select(patientuid, depressionscreen, cancer, advice, radiologicexam, electrocardiogram, mammogram, catheter) %>%
#   distinct() %>%
#   group_by(patientuid) %>%
#   summarize(across(
#     everything(),
#     ~sum(.)
#   )) %>%
#   mutate(across(
#     depressionscreen:catheter,
#     ~(ifelse(.>0,1,0))
#   ))
# 
# asian_patients <- only_single_asian %>%
#   left_join(patient_location_dedup) %>%
#   left_join(patient_outcomes_dedup %>% select(patientuid, hypertension, diabetes, depression, asthma)) %>%
#   left_join(patient_measurements_dedup %>% select(patientuid, diabetes_test = diabetes)) %>% 
#   left_join(patient_procedures_dedup %>% select(patientuid, depressionscreen, electrocardiogram)) %>% 
#   mutate(across(
#     hypertension:electrocardiogram,
#     ~replace_na(.,0)
#   )) %>%
#   select(patientuid, firstname = first, surname = last,dob,state,county,zip,tract,everything())
# 
# saveRDS(asian_patients,paste0(server_path,"disaggregation/asian_patients.rds"))
```

This dataset is not available because it contains PHI.

```{r}
asian_patients <- readRDS(paste0(server_path,"disaggregation/asian_patients.rds"))
```

# Individual accuracy

This for loop generates the primary bootstraps of the predictions. The final output is a list of 100 bootstraps that each contain the necessary information to create PR curves. See the bootstrap_afc() function and other helper functions in the helper script.

```{r}
geo_race_table_lst <- readRDS(paste0(github_path,"data/geography/geo_race_table.rds"))

load(paste0(github_path,"data/name_race_data/disagg_name_priors_main.rda"))

patients_categorized <- asian_patients %>% 
  mutate(
    category = case_when(
      surname %in% ssa_p_race_given_surname$name & surname %in% p_race_given_surname$name ~ "both",
      surname %in% ssa_p_race_given_surname$name ~ "ssa only",
      surname %in% p_race_given_surname$name ~ "wiki only",
      TRUE ~ "neither"
    )
  )

n_boot <- 100

tic()
bootstrap_pr_results <- foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
  bootstrap_afc(asian_patients, seed = i)
}
toc()

saveRDS(
  bootstrap_pr_results,
  paste0(github_result_path, "boot_results_main.rds")
)
```

## Table 3

This run specifically is for Table 3 in the paper, in which we identify the 4 key subsets of the validation set and calculate avg precision for each separately. Otherwise conceptually it's the same as running for the whole validation set.

```{r}
n_boot <- 100

load(paste0(github_path,"data/name_race_data/disagg_name_priors_main.rda"))

patients_categorized <- asian_patients %>% 
  mutate(
    category = case_when(
      surname %in% ssa_p_race_given_surname$name & surname %in% p_race_given_surname$name ~ "both",
      surname %in% ssa_p_race_given_surname$name ~ "ssa only",
      surname %in% p_race_given_surname$name ~ "wiki only",
      TRUE ~ "neither"
    )
  )

pr_lst <- data.frame()

tic()
pr_lst <- pr_lst %>% rbind(
  foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
    bootstrap_afc(patients_categorized %>% filter(category =="both"), seed = i)
  } %>% 
    mutate(category = "both")
)
toc()

tic()
pr_lst <- pr_lst %>% rbind( 
  foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
    bootstrap_afc(patients_categorized %>% filter(category =="ssa only"), seed = i)
  } %>% 
    mutate(category = "ssa only")
)
toc()

tic()
pr_lst <- pr_lst %>% rbind(
  foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
    bootstrap_afc(patients_categorized %>% filter(category =="wiki only"), seed = i)
  } %>% 
    mutate(category = "wiki only")
)
toc()

tic()
pr_lst <- pr_lst %>% rbind(
  foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
    bootstrap_afc(patients_categorized %>% filter(category =="neither"), seed = i)
  } %>% 
    mutate(category = "neither")
)
toc()

saveRDS(pr_lst, paste0(github_result_path,"boot_results_stratified_by_category.rds"))
```

## SI: Min/Max

```{r}
for(string in c("min","max")){
  
  load(paste0(github_path,"data/name_race_data/disagg_name_priors_",string,".rda"))
  
  n_boot <- 100

  tic()
  bootstrap_pr_results <- foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
    bootstrap_afc_bisg(asian_patients, seed = i)
  }
  toc()
  
  saveRDS(
    bootstrap_pr_results,
    paste0(github_result_path, "boot_results_",string,".rds")
  )
  
}
```

## SI: Geography

```{r}
load(paste0(github_path,"data/name_race_data/disagg_name_priors_main.rda"))

n_boot <- 100

for(geo in c("zip","tract","state")){
  
  tic()
  bootstrap_pr_results <- foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
    bootstrap_afc_bisg(asian_patients, seed = i, geography = geo)
  }
  toc()
  
  saveRDS(
    bootstrap_pr_results,
    paste0(github_result_path, "boot_results_",geo,".rds")
  )
  
}
```

## SI: BIFSG

```{r}
load(paste0(github_path,"data/name_race_data/disagg_name_priors_main.rda"))

n_boot <- 100

tic()
bootstrap_pr_results <- foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
  bootstrap_afc_bifsg(asian_patients, seed = i)
}
toc()

saveRDS(
  bootstrap_pr_results,
  paste0(github_result_path, "boot_results_bifsg.rds")
)
```

## SI: IPUMS

```{r}
load(paste0(github_path,"data/name_race_data/disagg_name_priors_ipums.rda"))

n_boot <- 100

tic()
temp <- foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
  bootstrap_afc_bisg(asian_patients, seed = i)
}
toc()

saveRDS(
  bootstrap_pr_results,
  paste0(github_result_path, "boot_results_ipums.rds")
)
```

## SI: Balanced

```{r}
n_boot <- 100

tic()
bootstrap_pr_results <- foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
  bootstrap_afc_balanced(asian_patients, seed = i)
}
toc()

saveRDS(
  bootstrap_pr_results,
  paste0(github_result_path, "boot_results_balanced.rds")
)
```

# PR tradeoff illustrations

```{r}
load(paste0(github_path,"data/name_race_data/disagg_name_priors_main.rda"))

p_race <- geo_race_table_lst$p_race_given_us
```

## Precision function

```{r}
bootstrap_precision <- function(patient_df, seed){
  
  set.seed(seed)
  b_patient_df <- patient_df %>% 
    slice_sample(n = nrow(.), replace = T)
  
  ssa_prediction <- b_patient_df %>% 
    predict_disagg_race(firstname = F, ssa = T) %>% 
    left_join(
      patients_categorized %>% 
        select(patientuid, raceeth, category),
      by="patientuid"
    )
  
  bisg_prediction <- b_patient_df %>% 
    select(patientuid, firstname, surname, state, county, zip, tract) %>% 
    predict_disagg_race(firstname = F) %>% 
    left_join(
      patients_categorized %>% 
        select(patientuid, raceeth, category),
      by="patientuid"
    )
  
  hybrid_prediction <- ssa_prediction %>% 
    filter(category %in% c("ssa only","wiki only")) %>% 
    rbind(
      bisg_prediction %>% 
        filter(!category %in% c("ssa only","wiki only"))
    )

  ssa_100 <- seq(0.79,0.99,0.01) %>% 
    map_dfr(function(x){
      
      unique(b_patient_df$raceeth) %>% 
        map_dfr(function(y){
          
          set.seed(seed)
        
          temp <- ssa_prediction %>%
            rename(race = all_of(y)) %>% 
            filter(race >= x) %>% 
            sample_n(pmin(nrow(.),100)) %>%
            filter(raceeth == y) %>%
            nrow() %>%
            as.data.frame() %>%
            rename(count = ".") %>%
            mutate(
              method = "SSA",
              type = x,
              raceeth = y,
              total = ssa_prediction %>%
                rename(race = all_of(y)) %>% 
                filter(race >= x) %>% 
                nrow()
            )
          
        })
      
    })

  bisg_100 <- seq(0.79,0.99,0.01) %>% 
    map_dfr(function(x){
      
      unique(b_patient_df$raceeth) %>% 
        map_dfr(function(y){
          
          set.seed(seed)
        
          temp <- bisg_prediction %>%
            rename(race = all_of(y)) %>% 
            filter(race >= x) %>% 
            sample_n(pmin(nrow(.),100)) %>%
            filter(raceeth == y) %>%
            nrow() %>%
            as.data.frame() %>%
            rename(count = ".") %>%
            mutate(
              method = "BISG",
              type = x,
              raceeth = y,
              total = bisg_prediction %>%
                rename(race = all_of(y)) %>% 
                filter(race >= x) %>% 
                nrow()
            )
          
        })
      
    })
  
  hybrid_100 <- seq(0.79,0.99,0.01) %>% 
    map_dfr(function(x){
      
      unique(b_patient_df$raceeth) %>% 
        map_dfr(function(y){
          
          set.seed(seed)
        
          temp <- hybrid_prediction %>%
            rename(race = all_of(y)) %>% 
            filter(race >= x) %>% 
            sample_n(pmin(nrow(.),100)) %>%
            filter(raceeth == y) %>%
            nrow() %>%
            as.data.frame() %>%
            rename(count = ".") %>%
            mutate(
              method = "Hybrid",
              type = x,
              raceeth = y,
              total = hybrid_prediction %>%
                rename(race = all_of(y)) %>% 
                filter(race >= x) %>% 
                nrow()
            )
          
        })
      
    })
  
  result <- rbind(ssa_100, bisg_100, hybrid_100) %>% mutate(seed = seed)
  
  return(result)
}
```

## Precision run

```{r}
n_boot <- 100

bootstrap_precision_results <- foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
    bootstrap_precision(asian_patients, seed = i)
}

saveRDS(bootstrap_precision_results, paste0(github_result_path, "bootstrap_precision_results.rds"))
```

## Recall function

```{r}
bootstrap_recall <- function(patient_df, seed){
  
  set.seed(seed)
  b_patient_df <- patient_df %>% 
    slice_sample(n = nrow(.), replace = T)
  
  ssa_prediction <- b_patient_df %>% 
    predict_disagg_race(firstname = F, ssa = T) %>% 
    left_join(
      patients_categorized %>% 
        select(patientuid, raceeth, category),
      by="patientuid"
    )
  
  bisg_prediction <- b_patient_df %>% 
    select(patientuid, firstname, surname, state, county, zip, tract) %>% 
    predict_disagg_race(firstname = F) %>% 
    left_join(
      patients_categorized %>% 
        select(patientuid, raceeth, category),
      by="patientuid"
    )
  
  hybrid_prediction <- ssa_prediction %>% 
    filter(category %in% c("ssa only","wiki only")) %>% 
    rbind(
      bisg_prediction %>% 
        filter(!category %in% c("ssa only","wiki only"))
    )
  
  result <- unique(b_patient_df$raceeth) %>% 
    map_dfr(function(y){
      
      total_actual <- b_patient_df %>% 
        filter(raceeth == y) %>% 
        nrow()
      
      ssa_recall <- 
        seq(0.01,0.1,0.01) %>%
        map_dfr(function(x){
    
          ssa_selected <- ssa_prediction %>% 
            rename(race = all_of(y)) %>% 
            filter(race > x)
          
          ssa_correct <- ssa_selected %>% 
            filter(raceeth == y)
          
          if(nrow(ssa_correct) > total_actual * 0.99) {
            
            set.seed(seed)
            
            ssa_minimum <- ssa_selected %>% 
              sample_n(nrow(.)) %>% 
              mutate(
                index = row_number(),
                race = ifelse(
                  raceeth == y,
                  1,
                  0
                ),
                cumul_race = cumsum(race)
              ) %>% 
              filter(cumul_race >= total_actual*0.99) %>% 
              pull(index) %>% 
              min()
            
            ssa <- data.frame(type = x) %>% 
              mutate(
                method = "SSA",
                outreach = ssa_minimum,
                total_actual = total_actual,
                oversample = outreach/total_actual,
                raceeth = y
              )
            
          } else {
            
            set.seed(seed)
            
            ssa_additional <- ssa_prediction %>% 
              rename(race = all_of(y)) %>%
              filter(race <= x) %>% 
              sample_n(nrow(.)) %>% 
              mutate(
                index = row_number(),
                race = ifelse(
                  raceeth == y,
                  1,
                  0
                ),
                cumul_race = cumsum(race)
              ) %>% 
              filter(cumul_race >= (total_actual*0.99 - nrow(ssa_correct))) %>% 
              pull(index) %>% 
              min()
            
            ssa <- data.frame(type = x) %>% 
              mutate(
                method = "SSA",
                outreach = nrow(ssa_selected) + ssa_additional,
                total_actual = total_actual,
                oversample = outreach/total_actual,
                raceeth = y
              )
            
          }
          
          return(ssa)
    
        })
      
      bisg_recall <- 
        seq(0.01,0.1,0.01) %>%
        map_dfr(function(x){
    
          bisg_selected <- bisg_prediction %>% 
            rename(race = all_of(y)) %>% 
            filter(race > x)
          
          bisg_correct <- bisg_selected %>% 
            filter(raceeth == y)
          
          if(nrow(bisg_correct) > total_actual * 0.99) {
            
            set.seed(seed)
            
            bisg_minimum <- bisg_selected %>% 
              sample_n(nrow(.)) %>% 
              mutate(
                index = row_number(),
                race = ifelse(
                  raceeth == y,
                  1,
                  0
                ),
                cumul_race = cumsum(race)
              ) %>% 
              filter(cumul_race >= total_actual*0.99) %>% 
              pull(index) %>% 
              min()
            
            bisg <- data.frame(type = x) %>% 
              mutate(
                method = "BISG",
                outreach = bisg_minimum,
                total_actual = total_actual,
                oversample = outreach/total_actual,
                raceeth = y
              )
            
          } else {
            
            set.seed(seed)
            
            bisg_additional <- bisg_prediction %>% 
              rename(race = all_of(y)) %>%
              filter(race <= x) %>% 
              sample_n(nrow(.)) %>% 
              mutate(
                index = row_number(),
                race = ifelse(
                  raceeth == y,
                  1,
                  0
                ),
                cumul_race = cumsum(race)
              ) %>% 
              filter(cumul_race >= (total_actual*0.99 - nrow(bisg_correct))) %>% 
              pull(index) %>% 
              min()
            
            bisg <- data.frame(type = x) %>% 
              mutate(
                method = "BISG",
                outreach = nrow(bisg_selected) + bisg_additional,
                total_actual = total_actual,
                oversample = outreach/total_actual,
                raceeth = y
              )
            
          }
          
          return(bisg)
    
        })
      
      hybrid_recall <- 
        seq(0.01,0.1,0.01) %>%
        map_dfr(function(x){
    
          hybrid_selected <- hybrid_prediction %>% 
            rename(race = all_of(y)) %>% 
            filter(race > x)
          
          hybrid_correct <- hybrid_selected %>% 
            filter(raceeth == y)
          
          if(nrow(hybrid_correct) > total_actual * 0.99) {
            
            set.seed(seed)
            
            hybrid_minimum <- hybrid_selected %>% 
              sample_n(nrow(.)) %>% 
              mutate(
                index = row_number(),
                race = ifelse(
                  raceeth == y,
                  1,
                  0
                ),
                cumul_race = cumsum(race)
              ) %>% 
              filter(cumul_race >= total_actual*0.99) %>% 
              pull(index) %>% 
              min()
            
            hybrid <- data.frame(type = x) %>% 
              mutate(
                method = "Hybrid",
                outreach = hybrid_minimum,
                total_actual = total_actual,
                oversample = outreach/total_actual,
                raceeth = y
              )
            
          } else {
            
            set.seed(seed)
            
            hybrid_additional <- hybrid_prediction %>% 
              rename(race = all_of(y)) %>%
              filter(race <= x) %>% 
              sample_n(nrow(.)) %>% 
              mutate(
                index = row_number(),
                race = ifelse(
                  raceeth == y,
                  1,
                  0
                ),
                cumul_race = cumsum(race)
              ) %>% 
              filter(cumul_race >= (total_actual*0.99 - nrow(hybrid_correct))) %>% 
              pull(index) %>% 
              min()
            
            hybrid <- data.frame(type = x) %>% 
              mutate(
                method = "Hybrid",
                outreach = nrow(hybrid_selected) + hybrid_additional,
                total_actual = total_actual,
                oversample = outreach/total_actual,
                raceeth = y
              )
            
          }
          
          return(hybrid)
    
        })
      
      rbind(ssa_recall, bisg_recall, hybrid_recall) %>% mutate(seed = seed)
      
    })
  
  return(result)
}
```

## Recall run

```{r}
n_boot <- 100

bootstrap_recall_results <- foreach (i = 1:n_boot, .combine= "rbind") %dopar% {
    bootstrap_recall(asian_patients, seed = i)
}

saveRDS(bootstrap_recall_results, paste0(github_result_path, "bootstrap_recall_results.rds"))
```

# Group prevalence

## Function

```{r}
get_prevalence <- function(patient_df, seed, type = "imbalanced"){
  
  outcomes <- c("hypertension","diabetes","diabetes_test","depression","depressionscreen","asthma")
  
  if(type == "imbalanced"){
    
    set.seed(seed)
    df <- patient_df %>% 
    slice_sample(n = nrow(.), replace = T)
    
  }
  if(type == "balanced"){
    
    set.seed(seed)
    
    df <- rbind(
      patient_df %>% 
      filter(raceeth == "asian_indian") %>% 
      slice_sample(n = 6073, replace = T),
      patient_df %>% 
        filter(raceeth == "chinese") %>% 
        slice_sample(n = 6218, replace = T),
      patient_df %>% 
        filter(raceeth == "filipino") %>% 
        slice_sample(n = 4100, replace = T),
      patient_df %>% 
        filter(raceeth == "japanese") %>% 
        slice_sample(n = 1059, replace = T),
      patient_df %>% 
        filter(raceeth == "korean") %>% 
        slice_sample(n = 2058, replace = T),
      patient_df %>% 
        filter(raceeth == "vietnamese") %>% 
        slice_sample(n = 2618, replace = T)
    )
    
  }
  
  ssa_prediction <- df %>% 
    select(patientuid, firstname, surname, state, county, zip, tract) %>% 
    predict_disagg_race(firstname = F, ssa = T) %>% 
    left_join(
      df %>% 
        select(patientuid, surname, all_of(outcomes)) %>% 
        distinct(),
      by="patientuid"
    ) %>% 
    left_join(
      patients_categorized %>% select(patientuid,category)
    )
  
  bisg_prediction <- df %>% 
    select(patientuid, firstname, surname, state, county, zip, tract) %>% 
    predict_disagg_race(firstname = F) %>% 
    left_join(
      df %>% 
        select(patientuid, surname, all_of(outcomes)) %>% 
        distinct(),
      by="patientuid"
    ) %>% 
    left_join(
      patients_categorized %>% select(patientuid,category)
    )
  
  hybrid_prediction <- ssa_prediction %>% 
    filter(category %in% c("ssa only","wiki only")) %>% 
    rbind(
      bisg_prediction %>% 
        filter(!category %in% c("ssa only","wiki only"))
    )
  
  result <- df %>% 
    select(raceeth,all_of(outcomes)) %>%
    mutate(type = "observed") %>% 
    pivot_longer(
      -c(type,raceeth),
      names_to = "outcome",
      values_to = "result"
    ) %>%
    group_by(type, raceeth, outcome) %>%
    summarize(
      n = sum(result),
      total = n()
    ) %>%
    mutate(
      prev = n/total,
      sample = seed
    ) %>%
    rbind(
      ssa_prediction %>% 
        select(-patientuid, -surname, -category) %>% 
        pivot_longer(
          -all_of(outcomes),
          names_to = "raceeth",
          values_to = "n"
        ) %>% 
        pivot_longer(
          -c(raceeth,n),
          names_to = "outcome",
          values_to = "result"
        ) %>% 
        group_by(raceeth, outcome) %>%
        summarize(
          n = sum(n*result,na.rm=T),
          total = sum(n,na.rm=T)
        ) %>% 
        mutate(
          prev = n/total,
          sample = seed,
          type = "SSA weighted"
        ),
      bisg_prediction %>% 
        select(-patientuid, -surname, -category) %>% 
        pivot_longer(
          -all_of(outcomes),
          names_to = "raceeth",
          values_to = "n"
        ) %>% 
        pivot_longer(
          -c(raceeth,n),
          names_to = "outcome",
          values_to = "result"
        ) %>% 
        group_by(raceeth, outcome) %>%
        summarize(
          n = sum(n*result,na.rm=T),
          total = sum(n,na.rm=T)
        ) %>% 
        mutate(
          prev = n/total,
          sample = seed,
          type = "BISG weighted"
        ),
      hybrid_prediction %>% 
        select(-patientuid, -surname, -category) %>% 
        pivot_longer(
          -all_of(outcomes),
          names_to = "raceeth",
          values_to = "n"
        ) %>% 
        pivot_longer(
          -c(raceeth,n),
          names_to = "outcome",
          values_to = "result"
        ) %>% 
        group_by(raceeth, outcome) %>%
        summarize(
          n = sum(n*result,na.rm=T),
          total = sum(n,na.rm=T)
        ) %>% 
        mutate(
          prev = n/total,
          sample = seed,
          type = "Hybrid weighted"
        )
    ) %>% 
    ungroup()
  
}
```

## Run

```{r}
load(paste0(github_path,"data/name_race_data/disagg_name_priors_main.rda"))

patients_categorized <- asian_patients %>% 
  mutate(
    category = case_when(
      surname %in% ssa_p_race_given_surname$name & surname %in% p_race_given_surname$name ~ "both",
      surname %in% ssa_p_race_given_surname$name ~ "ssa only",
      surname %in% p_race_given_surname$name ~ "wiki only",
      TRUE ~ "neither"
    )
  )
  
n_boot <- 100

prevalence_results <- foreach (i = 1:n_boot, .combine = "rbind") %dopar% {
  get_prevalence(asian_patients, seed = i)
}

saveRDS(prevalence_results, paste0(github_result_path,"prevalence_results.rds"))
```

## SI: Balanced

```{r}
n_boot <- 100

prevalence_results <- foreach (i = 1:n_boot, .combine = "rbind") %dopar% {
  get_prevalence(asian_patients, seed = i, type = "balanced")
}

saveRDS(prevalence_results, paste0(github_result_path,"prevalence_results_balanced.rds"))
```